---
title: "scSNVis"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

```{r eruptions1, echo = FALSE}
library(Seurat)
library(ggplot2)
library(data.table)
library(tidyverse)


sample_id <- 'SRR10156295'
Gene_Seurat <- readRDS('SRR10156295_done.rds')

#SingleR
library(SingleR)
rna_re <- BlueprintEncodeData()
b <- GetAssayData(Gene_Seurat)
cluster <- Gene_Seurat@active.ident
result_cluster <- SingleR(test = b, ref = rna_re, labels = rna_re$label.fine, method="cluster", clusters = cluster)
Gene_Seurat[["SingleR.cluster.labels"]] <-
  result_cluster$labels[match(Gene_Seurat[[]]["seurat_clusters"]$seurat_clusters, rownames(result_cluster))]
DimPlot(Gene_Seurat, group.by =  "SingleR.cluster.labels", reduction = "umap", label = TRUE) + labs(title = sample_id)

```


```{r eruptions2,  echo=FALSE}
snv_choose <- '1:16640676_A>G'
snv_matrix <- data.frame(fread ('SRR10156295_dedupped_wasp_Aligned.sortedByCoord.out_VAF_matrix.tsv'), row.names = 1)
snv_choose_matrix <- snv_matrix[row.names(snv_matrix) %in% snv_choose,]
#snv_choose <- names(snv_choose_matrix)[which(sapply(snv_choose_matrix, function(x) strsplit(x,':')[[1]][2] !=0))]
names(snv_choose_matrix) <- paste0(names(snv_choose_matrix), '_1')
#snv_choose_matrix[is.na(snv_choose_matrix)] <- '0'
snv_choose_matrix <- snv_choose_matrix[names(snv_choose_matrix) %in% rownames(Gene_Seurat@meta.data)]
gene_seurat_matrix <- Gene_Seurat@meta.data %>% rownames_to_column()
Gene_Seurat<-AddMetaData(Gene_Seurat,Gene_Seurat@reductions$umap@cell.embeddings,col.name = colnames(Gene_Seurat@reductions$umap@cell.embeddings))
tmp <- Gene_Seurat@meta.data %>% rownames_to_column()

snv_choose_matrix <- as.data.frame(t(snv_choose_matrix)) %>% rownames_to_column()
choose_seurat_matrix <- left_join(tmp, snv_choose_matrix, by = "rowname")
class_avg <- choose_seurat_matrix %>%
  group_by(SingleR.cluster.labels) %>%
  summarise(
    UMAP_1 = median(UMAP_1),
    UMAP_2 = median(UMAP_2)
  )

```


```{r eruptions3}

snv_idx <- length(gene_seurat_matrix)
choose_seurat_matrix$choose <- 'NA'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] == '0'] <- '0'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] > 0 & choose_seurat_matrix[[snv_choose]] <=0.2] <- '0-0.2'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] > 0.2 & choose_seurat_matrix[[snv_choose]] <=0.4] <- '0.2-0.4'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] > 0.4 & choose_seurat_matrix[[snv_choose]] <= 0.6] <- '0.4-0.6'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] > 0.6 & choose_seurat_matrix[[snv_choose]] <=0.8] <- '0.6-0.8'
choose_seurat_matrix$choose[choose_seurat_matrix[[snv_choose]] > 0.8 & choose_seurat_matrix[[snv_choose]] <=1] <- '0.8-1'

ggplot(choose_seurat_matrix , aes(x = UMAP_1, y=UMAP_2)) +
  geom_point(aes(color= factor(choose)), alpha = 0.5) +
  geom_text(aes(label = SingleR.cluster.labels), data = class_avg) + 
  labs(title = paste0(snv_choose, '_', sample_id)) +
  theme(text=element_text(family="Arial",size=16)) +
  theme(panel.background = element_rect(fill='white', colour='black'), 
        panel.grid=element_blank(), 
        axis.ticks = element_line(color='black'), 
        axis.line = element_line(colour = "black"), 
        axis.title.x=element_text(colour='black', size=12, face = "italic"),
        axis.title.y=element_text(colour='black', size=12, face = "italic"),
        axis.text=element_text(colour='black',size=12,face = "italic"),
        #legend.title=element_blank(),
        legend.text=element_text(colour='black', size=12),
        legend.key=element_blank()) + 
  theme(plot.title = element_text(size=18,colour = "black",face = "italic")) +
  scale_color_manual(values = c('darkgrey','pink','red','red1','red2','red3','grey') ,  name = 'VAF')  

```